%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nelson Bruno Andrés Moreno Cabañas} \\ \vspace{3pt}
    \large \textit{Data Scientist | Machine Learning Engineer} \\ \vspace{3pt}
    \small +56 997200464 $|$ \href{mailto:nelson.moreno.cabanas@gmail.com}{\underline{nelson.moreno.cabanas@gmail.com}} $|$ 
    \href{https://linkedin.com/in/nelson-moreno-cabanas/}{\underline{linkedin.com/in/nelson-moreno-cabanas}} $|$
    \href{https://github.com/Bruno-Moreno}{\underline{github.com/Bruno-Moreno}}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
Data Scientist with over 3 years of experience building end-to-end data science projects across different industries. My mathematical background enables me to solve technical problems with high precision and attention to detail. My experience among different industries has provided me with a broad understanding of different collaboration strategies and effective communication skills. 

\vspace{0.3cm}

I am seeking a challenging job with several growth opportunities. I am always eager to learn and not afraid to step out of my comfort zone.

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, R} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Snowflake, Airflow} \\
     \textbf{Libraries}{: SciPy, Pandas, PySpark, Scikit-Learn, Tensorflow, PyTorch} \\
     \textbf{Data Visualization}{: Matplotlib, Seaborn, Plotly, Power BI} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Data Scientist}{Sep. 2023 -- Current}
      {Rappi $|$ Rappicard by Itaú - Digital Credit Card}{Santiago, Chile}
      \resumeItemListStart
      \resumeItem{Implemented a segmentation model that enabled tracking of client's activity, behavior, satisfaction and churn propensity. The retention actions across different segments resulted in a churn rate decrease and a NPS improvement.}
      \resumeItem{Worked on an acquisition model for Rappi's top users and successfully increased 2x the number of contracts in that group.}
      \resumeItem{Tested new communication strategies with the marketing team and measured their statistical effectiveness. This AB testing lead to user's personalization of communications.}
      \resumeItem{Created ETL processes to address business needs using Airflow, delivering processed data to the BI team for their reports.}
    \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{Aug 2022 - Sep 2023}
      {Consorcio - Bank and Insurance Company}{Santiago, Chile}
      \resumeItemListStart
        \resumeItem{Successfully created customer propensity models for all Consorcio's products, resulting in a significant reduction in the cost of acquisition. I developed a product churn prediction model that achieved a 5\% reduction in churn rate every month, as well as a risk measurement model that improved the previous model AUC by 10pp.}
        \resumeItem{MLOps practices were implemented in collaboration with AWS for monitoring and maintaining machine learning models using Sagemaker Studio. These practices are now implemented through the entire Data \& Analytics area.}
        \resumeItem{Led a team of four people during transitional periods in the area, ensuring that each person's projects continued to develop without interruption.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{Dec 2021 - Aug 2022}
      {IC Innovations - CHASKi: Wearable sport device for athletes}{Santiago, Chile}
      \resumeItemListStart
        \resumeItem{Responsible for data processing and algorithm development for a wearable device designed to measure athlete's respiratory rates during exercise.}
        \resumeItem{Tested the algorithms against clinical experiments and achieved 92\% accuracy in determining ventilatory thresholds.}
        \resumeItem{Created the first customized report delivered to athletes as the MVP of the product.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Intern}{Dec 2020 - Jan 2021}
      {Alaya - Data Science Consulting}{Santiago, Chile}
      \resumeItemListStart
        \resumeItem{Develop an anomaly detection, satiety period monitoring and biomass estimation software for salmon in captivity using image processing and deep learning tools. This project enabled Alaya to enter the aquaculture market.}
      \resumeItemListEnd

      \resumeSubheading
      {Data Analyst Intern}{Dec 2019 - Feb 2020}
      {Deloitte - Consulting, Financial Advisory, Risk Advisor}{Santiago, Chile}
      \resumeItemListStart
        \resumeItem{Provision estimation for banks according to the BASEL III manual.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {Master's Degree, Data Science (Grade $6.7/7.0$) \href{https://repositorio.uchile.cl/handle/2250/197408}{\underline{Master's Thesis}}}{2022 - 2023}
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {Bachelor's Degree, Mathematical Engineer (Grade $6.7/7.0$)}{2017 - 2023}
  \resumeSubHeadingListEnd

%-----------ACADEMIC----------- 

 \section{Academic}
  \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
     \textbf{Teacher Assistant - University of Chile} \\
     Lectures and content creation:\\ Machine Learning (1), Statistics (2), Linear Algebra (1), Ordinary Differential Equations (2), Calculus (1), Probabilities and Statistics (4). \\
    }}
    \small{\item{
     \textbf{CEIMAT Director - University of Chile} \\
     Director of the Mathematical Engineering Student Center at the Faculty of Physical and Mathematical Sciences. 
    }}
 \end{itemize}

 %-----------LANGUAGES-----------

\section{Languages}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English} \\
     \textit{Full professional proficiency} \\
    }}
    \small{\item{
     \textbf{Spanish} \\
     \textit{Native} \\
    }}
 \end{itemize}

 %-----------Certifications-----------
 
\section{Certifications}
  \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
     \textbf{Generative AI Fundamentals - Google} \\
     \textit{Issued Jan 2024} \\
    }}
    \small{\item{
     \textbf{Apache Airflow Fundamentals - Platzi} \\
     \textit{Issued Nov 2023} \\
    }}
    \small{\item{
     \textbf{AWS Certified Cloud Practitioner - Udemy} \\
     \textit{Issued Jan 2023} \\
    }}
    \small{\item{
     \textbf{B2: Upper Independent - TOEFL ITP} \\
     \textit{Issued Jan 2019, Expires Jun 2021} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
